Measuring Individual Partisan Harm in Redistricting

### 2021-09-11 paper/paper.Rmd

Decades of literature on redistricting have focused on the fairness to parties.
This literature defers to symmetric outcomes for parties, commonly referred to as partisan symmetry [@katz2020].
Partisan symmetry is a useful idea which greatly improves academic understanding of the redistricting process.
Why is it hard?
Understanding the redistricting process requires a feasible and reliable understanding of the counterfactual set of redistricting plans.
Early methodologies for simulating plans relied on randomness to generate many different plans and enhanced understanding of redistricting greatly [@ciri:darl:orou:00; @chen:rodd:13; @deford2019].
These methods greatly enhanced the understanding of redistricting within contexts of a particular state with set populations.
Yet, without a known target distribution, these heuristic approaches to simulation fall do not offer necessary guarantees for confidence in the simulated plans to represent the total space of possible plans [@fifield2020essential].
Recent advances in Markov Chain methods as applied to redistricting allow us move beyond simulation towards sampling plans from this definable space [@fifield2020mcmc; @carter2019; @deford2019; @mccartan2020].

@@

```{r nj-vars, fig.cap="Various measures for an ensemble of New Jersey districting plans.", fig.width=6.5, fig.height=6.5}
#include_graphics(here("out/nj_vars.pdf"))
```

>>>>

Decades of literature on redistricting have focused on the fairness to parties.
This literature defers to symmetric outcomes for parties, commonly referred to as partisan symmetry [@katz2020].
Partisan symmetry is a useful idea which greatly improves academic understanding of the redistricting process.

Understanding the redistricting process requires a feasible and reliable understanding of the counterfactual set of redistricting plans.
Early methodologies for simulating plans relied on randomness to generate many different plans and enhanced understanding of redistricting greatly [@ciri:darl:orou:00; @chen:rodd:13; @deford2019]. These methods greatly enhanced the understanding of redistricting within contexts of a particular state with set populations. Yet, without a known target distribution, these heuristic approaches to simulation fall do not offer necessary guarantees for confidence in the simulated plans to represent the total space of possible plans [@fifield2020essential]. Recent advances in Markov Chain methods as applied to redistricting allow us move beyond simulation towards sampling plans from this definable space [@fifield2020mcmc; @carter2019; @mccartan2020].

@@

Figure \ref{fig:nj-maps} shows the baseline Democratic vote share by precinct, along with two hypothetical gerrymanders of the state, which were generated using the short-burst optimization approach of @cannon2020.
